---
title: "p8015_hw5_tl2882"
author: "Tian Li"
date: 2018-11-07
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

# Problem 1

## Read data
```{r read_data}
read_data = function(file){
  read.csv(str_c("./data/", as.character(file)))
}

file_name = list.files("./data")
output = purrr::map_df(file_name, read_data)
```

## Tidy data
```{r tidy_data}
data = output %>%
  mutate(input = file_name) %>% 
  separate(input, into = c("arm", "id"), sep = "_") %>% 
  mutate(id = str_replace(id, ".csv", "")) %>% 
  gather(key = "week", value = "value", week_1:week_8) %>% 
  mutate(week = str_replace(week, "week_", ""))

head(data)
```

## Spaghetti plot
```{r Spaghetti_plot}
data %>%
  mutate(week = as.numeric(week)) %>% 
  ggplot(aes(x = week, y = value, color = id)) +
    geom_line() +
    facet_grid(~arm) + 
    labs(title = "Observations on each subject over time in different groups")
```

This is the spaghetti plot showing observations on each subject over time.

### Comment
1. In experimental group, most values tend to grow over time in general; In control group, most values don't have many changes over time in general.

2. Relatively, most values in experimental group are higher than those in control group.

# Problem 2

## Read data
```{r read_data2}
data2 = read.csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")

head(data2)
```
The dimension of the raw data is ```r dim(data2)``` (number of observations, variables).

Vriable names are ```r variable.names(data2)```.

## Count homicides
```{r count_homicides}
data_count = data2 %>% 
  unite(city_state, city, state, sep = ", ") %>% 
  group_by(city_state) %>% 
  summarise(n_unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest")),
            n_total = n())

head(data_count)
```

"data_count" is the dataframe which shows the total number of homicides and the number of unsolved homicides according to cities.

## Proportion test

### Baltimore
```{r test_bal}
data_bal = 
  data_count %>% 
  filter(city_state == "Baltimore, MD")

prop_bal = prop.test(data_bal$n_unsolved, data_bal$n_total)

prop_bal %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
```

For the city of Baltimore, MD, the estimate proportion is 0.646, and the CI is (0.628, 0.663).

### All cities
```{r test_all}
prop_all = 
  data_count %>% 
  mutate(tests = purrr::map2(.x = data_count$n_unsolved, .y = data_count$n_total,
                                ~broom::tidy(prop.test(.x, .y)))) %>% 
  unnest() %>% 
  select(city_state, estimate, conf.low, conf.high)

head(prop_all)
```

"prop_all" is the tidy dataframe with estimated proportions and CIs for each city.

## Bar lot
```{r bar_plot}
prop_all %>% 
  filter(city_state != "Tulsa, AL") %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, weight = estimate)) +
    geom_bar() + 
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.5) +
    labs(title = "The estimates and CIs for each city", y = "Proportion") +
    theme(axis.text.x = element_text(angle = -90))
```

This is the bar plot that shows the estimates and CIs for each city.
